DATA 621 Homework #3

### 2019-10-29 hw3/HW3_Adam.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA, message=FALSE, warning=FALSE)
library(tidyverse)
library(kableExtra)
library(corrplot)
library(caret)
library(rpart)
library(rpart.plot)
library(Amelia)
# Thank you Stack Overflow!
# A Prefix nulling hook.

@@

## Data Preparation
```{r}
ggplot(train, aes(rad , nox, color=as.factor(target))) +
  geom_point()
```

@@

for (i in 1:6){
  p <- plot(fit, data = "test", tree=i)
  print(p)
}
```

```{r}
fit <- rpart(target ~ ., method="class", data=train)
rpart.plot(fit)
```

```{r}
get_high_nox <- function(x){
  if(x > 0.53){
    return("High")
  } else {
    return("Low")
  }
}

get_divider <- function(x, y){
  if(x < 10 & y < 0.6){
    return(1)
  } else {
    return(0)
  }
}

train <- train %>%
  rowwise() %>%
  mutate(high_nox = get_high_nox(nox),
         divider = get_divider(rad, nox))

test <- test %>%
  rowwise() %>%
  mutate(high_nox = get_high_nox(nox),
         divider = get_divider(rad, nox))
```

## Feature Engineering
```{r}

@@

```{r}
baseline <- glm(target ~ nox, family = binomial(link = "logit"), train)
summary(baseline)
test$baseline <- ifelse(predict(baseline, test) < 0.5, 0, 1)
test$baseline_yhat <- predict(baseline, test)
confusionMatrix(factor(test$baseline), factor(test$target))
```

```{r}
model1 <- glm(target ~ high_nox + indus, family = binomial(link = "logit"), train)
summary(model1)
test$model1 <- ifelse(predict(model1, test) < 0.5, 0, 1)
test$model1_yhat <- predict(model1, test)
confusionMatrix(factor(test$model1), factor(test$target))
```

```{r}
model2 <- glm(target ~ divider, family = binomial(link = "logit"), train)
summary(model2)
test$model2 <- ifelse(predict(model2, test) < 0.5, 0, 1)
test$model2_yhat <- predict(model2, test)
confusionMatrix(factor(test$model2), factor(test$target))
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA, message=FALSE, warning=FALSE)
library(tidyverse)
library(kableExtra)
library(corrplot)
library(caret)
library(Amelia)
# Thank you Stack Overflow!
# A Prefix nulling hook.

@@

## Data Preparation

```{r}
baseline <- glm(target ~ nox, family = binomial(link = "logit"), train)
summary(baseline)
test$baseline <- ifelse(predict.glm(baseline, test,"response") >= 0.5,1,0)
cm <- confusionMatrix(factor(test$baseline2), factor(test$target),"1")
results <- tibble(model = "baseline",predictors = 1,F1 = cm$byClass[7],
                  deviance=baseline$deviance, 
                  r2 = 1 - baseline$deviance/baseline$null.deviance,
                  aic=baseline$aic)
cm
```

Our baseline model is ok with an F1 score of `r cm$byClass[7]`.

Now we will try adding all other variables and work backwards to eliminate non-significant predictors:

```{r}
fullmodel <- glm(target ~ nox + dis, family = binomial(link = "logit"), train)
summary(fullmodel)
test$fullmodel <- ifelse(predict.glm(fullmodel, test,"response") < 0.5, 0, 1)
cm <- confusionMatrix(factor(test$fullmodel), factor(test$target),"1")
results <- rbind(results,tibble(model = "fullmodel",
                                predictors = 12,F1 = cm$byClass[7],
                                deviance=fullmodel$deviance, 
                                r2 = 1-fullmodel$deviance/fullmodel$null.deviance,
                                aic=fullmodel$aic))
cm
```

The full model has an F1 score is `r cm$byClass[7]`, which is a bit higher than before. However, the new variable doesn't seem to be significant.

After some backward elimination of non-significant predictor variables, we arrive at the following model:

```{r}
model1 <- glm(target ~ . -tax -rm -chas - age -zn -indus, 
              family = binomial(link = "logit"), 
              train)
summary(model1)
test$model1 <- ifelse(predict.glm(model1, test,"response") < 0.5, 0, 1)
cm <- confusionMatrix(factor(test$model1), factor(test$target),"1")
results <- rbind(results,tibble(model = "model1",
                                predictors = 6,F1 = cm$byClass[7],
                                deviance=model1$deviance, 
                                r2 = 1-model1$deviance/model1$null.deviance,
                                aic=model1$aic))
cm
```

Looking at our models together, `model1` looks like the best so far based on highest F1 score and lowest deviance & AIC.

```{r}
kable(results)
```

@@

for (i in 1:6){
  p <- plot(fit, data = "test", tree=i)
  print(p)
}

@@
